manuscript - APP

### 2018-10-17 R/manuscript_app.Rmd
additional changes to the manuscript

```{r Figure 2}
traj_k64 <- read.table(file.path(data_pth, "exp1a", "trajectories", "T001_64_rest4.csv")) %>% select(x = V1,y = V2) %>% as_data_frame()
p1 <- traj_k64 %>% ggplot(aes(x,y)) + geom_point() + theme(aspect.ratio = 1) + xlim(-15,15)+ylim(-15,15) +
  ggtitle("Ballistic-like")

traj_k4 <- read.table(file.path(data_pth, "exp1a", "trajectories", "T001_4_rest4.csv")) %>% select(x = V3,y = V4) %>% as_data_frame()
p2 <- traj_k4 %>% ggplot(aes(x,y)) + geom_point() + theme(aspect.ratio = 1) + xlim(-15,15)+ylim(-15,15)+
  ggtitle("Brownian-like")
gridExtra::grid.arrange(p1,p2, ncol = 2)

ggsave(file.path(plot_pth, "Figure2_ballistic.png"), p1, width = 6, height = 6)
ggsave(file.path(plot_pth, "Figure2_brownian.png"), p2, width = 6, height = 6)
ggsave(file.path(plot_pth, "Figure2_ballistic.eps"), p1, width = 6, height = 6)
ggsave(file.path(plot_pth, "Figure2_brownian.eps"), p2, width = 6, height = 6)
```

@@

>>>>

```{r Figure 2}
data_pth <- here::here("..","data", "exp1b", "trajectories")

traj_k64_raw <- read.table(file.path(data_pth, "T001_4_rest64.csv")) %>% 
  as_data_frame() %>% 
  mutate(t=1:n())

trajx <- traj_k64_raw %>% 
  select(V1,V3,V5,V7,V9,V11,V13,V15,t) %>% 
  gather(key = "object", value = "xcoord", -t) %>% 
  mutate(object = recode(object, V1 = "o1", V3 = "o2", V5 = "o3", V7 = "o4", V9 = "o5", V11 = "o6", V13 = "o7", V15 = "o8"))

trajy <- traj_k64_raw %>% 
  select(V2,V4,V6,V8,V10,V12,V14,V16,t) %>% 
  gather(key = "object", value = "ycoord", -t) %>% 
  mutate(object = recode(object, V2 = "o1", V4 = "o2", V6 = "o3", V8 = "o4", V10 = "o5", V12 = "o6", V14 = "o7", V16 = "o8"))

traj_k64 <- trajx %>% 
  left_join(trajy, by = c("t", "object")) %>% 
  mutate(type = if_else(object == "o1", "target", "distractor"))

p1 <- traj_k64 %>% 
  filter(t > 10) %>%
  filter(object %in% c("o1","o2","o7","o3","o5")) %>% 
  ggplot(aes(xcoord, ycoord, group = object)) + 
  geom_path(size = 0.5) + 
  theme(aspect.ratio = 1) + 
  xlim(-15,15) +
  ylim(-15,15) +
  #scale_linetype_manual(values=c("solid", "solid")) + 
  geom_point(data = traj_k64 %>% filter(t==max(t), object %in% c("o2","o7","o3","o5")), aes(xcoord, ycoord, fill = type), size = 4, shape = 16, show.legend=FALSE) +
  geom_point(data = traj_k64 %>% filter(t==max(t), object %in% c("o1")), aes(xcoord, ycoord, fill = type), size = 4, shape = 1, show.legend=FALSE) +
  #geom_point(data = traj_k64 %>% filter(t==max(t),object %in% c("o1","o2","o7","o4","o5")), aes(xcoord, ycoord, fill = type), size = 4, shape = 16, show.legend=FALSE) +
  guides(color = FALSE) +
  xlab("x [deg]") +
  ylab("y [deg]") +
  ggtitle(expression("Target's "*kappa~"= 4; Distractors' "*kappa~"= 64")) +
  theme(plot.title = element_text(hjust = 0.5))
p1
ggsave(here::here("..", "plots", "Figure2.png"), p1, width = 6, height = 6)

ggsave(here::here("..", "plots", "Figure2_t1.eps"), plot_trial_frame(t = 1), width = 6, height = 6)

maxt <- traj_k64$t %>% max()

ggsave(here::here("..", "plots", "Figure2_tmax.eps"), plot_trial_frame(t = maxt), width = 6, height = 6)

# final version was adjusted in inkscape 
```

@@

## Reaction times

```{r}
df_exp1a %>% 
  group_by(restk2) %>% 
  filter(accuracy == 1) %>% 
  lmerTest::lmer(responseTime~type+(1|subject),.) %>% lmerTest::summary() %>% broom::tidy()
